### 2013-07-16 Tex/chapters/results.tex
kleine Ergänzung zu den Abweichungen des beta

    \(\beta\) seem to be a bit too big, but they are close enough to the
    expectations to be consistent.

@@

    disordered Ising model is in the same universality class as the
    standard Ising ferromagnet.

>>>>

    \(\beta\) seem to be a bit too big -- especially for the Relative
    Neighborhood grap -- but they are close enough to the expectations
    to be consistent. At least the expectations are always within two
    times the uncertainty.

@@

    disordered Ising model is for every \(\sigma\)in the same universality
    class as the standard Ising ferromagnet.
